---
title: "Wenjing Sun_SNA HW2"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(igraph)
library(NetData)
library(data.table)
rm(list = ls(all = TRUE))
setwd("D:/social network analysis/HW2")
```

```{r}
data(studentnets.S641, package = "NetData")
```

```{r}
# check objects
ls()
```
#Question 1
Return to the classrom exercise featuring the S641 data, which can be accessed with
data(studentnets.S641, package = "NetData"). Generate indegree, outdegree, undirected
closeness (as opposed to the directed version in the example), betweenness, and undirected
eigenvector centrality statistics for each individual the task network. Compute the
correlations of the five centrality measures you generate in the task talk network with the
same measures for each individual in the socializing network. Which measures in the task
network are most closely related to those in the socializing network? What sort of substantive
story can you derive from all of these results?

## answer: Closeness,betweenneww, outdegree are most closely related in two networks. The both networks have similar structures. The probability is high that People who have task_ties also have social ties, and vice versa. 
```{r}
# reduce to non-zero edges and build a graph object
task_nonzero_edges = subset(task_df, task_tie > 0)

 
task = graph.data.frame(task_nonzero_edges) 


# plot each network
plot.igraph(task, layout=layout.fruchterman.reingold, edge.arrow.size=.5)

# in a directed network, we can think of in-closeness centrality as the average number of steps needed to get to a node from all the other nodes. out-closeness centrality measures the same thing with the directionality reversed

#indegree of task
indegree_task<-degree(task, mode = "in")
indegree_task

#outdegree of task
outdegree_task<-degree(task, mode = "out", loops = TRUE, normalized = FALSE)
outdegree_task

# closeness centrality undirected task
allcloseness_task = closeness(task, mode='all')
allcloseness_task

# betweenness centrality measures the number of shortest paths going through a specific vertex and is returned by the betweenness() function
betweenness_task = betweenness(task,directed=TRUE)
betweenness_task

#undirected eigenvector centrality
task_eigen<-eigen_centrality(task, directed = FALSE)$vector
task_eigen
```
```{r}
# reduce to non-zero edges and build a graph object
social_nonzero_edges = subset(social_df, social_tie > 0)
 
social = graph.data.frame(social_nonzero_edges) 

# plot each network
plot.igraph(social, layout=layout.fruchterman.reingold, edge.arrow.size=.5)

# in a directed network, we can think of in-closeness centrality as the average number of steps needed to get to a node from all the other nodes. out-closeness centrality measures the same thing with the directionality reversed

#indegree of social
indegree_social<-degree(social, mode = "in", loops = TRUE, normalized = FALSE)
indegree_social

#outdegree of social
outdegree_social<-degree(social, mode = "out", loops = TRUE, normalized = FALSE)
outdegree_social

# closeness centrality undirected social
allcloseness_social = closeness(social, mode='all')
allcloseness_social

# betweenness centrality measures the number of shortest paths going through a specific vertex and is returned by the betweenness() function
betweenness_social = betweenness(social,directed=TRUE)
betweenness_social

#undirected eigenvector centrality
social_eigen<-eigen_centrality(social, directed = FALSE)$vector
social_eigen
```
```{r}
#correlation

fun_cor<-function(x){
  c<-c()
  for(i in 1:22){
    for (j in 1:length(x)){
      if (as.numeric(rownames(data.frame(x)))[j]==i)
        c[i]<-x[j]
    }
  }
  return (c)
}


cor(fun_cor(indegree_social),fun_cor(indegree_task),use = "complete.obs")
cor(fun_cor(outdegree_social),fun_cor(outdegree_task),use = "complete.obs")
cor(fun_cor(allcloseness_social),fun_cor(allcloseness_task),use = "complete.obs")
cor(fun_cor(betweenness_social),fun_cor(betweenness_task),use = "complete.obs")
cor(fun_cor(social_eigen),fun_cor(task_eigen),use = "complete.obs")

```

# Question 2
Remaining with the classroom network, suppose that a tie is strong if it is above the mean
strength for that type, conditional on the tie existing. Consider both social and task ties
as being a part of the same network. Under this definition, does the network satisfy Strong
Triadic Closure? 
Now suppose that a tie is strong if it is above the median strength for that
type, conditional on the tie existing. Under this definiton, does the network satisfy Strong
Triadic Closure? What conclusions can you draw from these results?

## answer: Under the definition using mean, the network does not satisfy strong triadic closure. There are 5 groups of nodes with 2 strong and 0 relationships among the nodes.Under the definition using median, the network does not satisfy strong triadic closure. There are 37 groups of nodes with 2 strong and 0 relationships among the nodes.Details are after the codes below. Whether a network satisfies strong triadic closure can depend on the structure of data and the definition of strong/weak relationship.

```{r}
full = s641_full_data_frame
for (i in 1:nrow(full)){
  if (full[i,3]>0)
    full[i,"social_1"]=1
  else
    full[i,"social_1"]=0
}

for (i in 1:nrow(full)){
  if (full[i,4]>0)
    full[i,"task_1"]=1
  else
    full[i,"task_1"]=0
}

mean_social<-sum(full[3])/sum(full["social_1"])
mean_task<-sum(full[4])/sum(full["task_1"])


for (i in 1:nrow(full)){
  if (full[i,3]>mean_social)
    full[i,"social_new"]=20
  else if (full[i,3]<=mean_social&full[i,3]!=0)
    full[i,"social_new"]=1
  else
    full[i,"social_new"]=full[i,3]
}


for (i in 1:nrow(full)){
  if (full[i,4]>mean_task)
    full[i,"task_new"]=20
  else if (full[i,4]<mean_task&full[i,4]!=0)
    full[i,"task_new"]=1
  else
    full[i,"task_new"]=full[i,4]
}


for (i in 1:nrow(full)){
  if (full[i,"social_new"]>=full[i,"task_new"])
    full[i,"triad"]=full[i,"social_new"]
  else
    full[i,"triad"]=full[i,"task_new"]
}

full_matrix<-matrix(nrow=22,ncol=22)
for (i in 1:nrow(full)){
    full_matrix[full[i,1],full[i,2]]<-full[i,9]
}
mean_s<-0
mean_s_matrix<-matrix(ncol=3)
for (i in 1:22){
  for (j in 1:22){
    for (k in 1:22){
      if(j>k)
        if (full_matrix[i,j]==20&full_matrix[i,k]==20 & full_matrix[j,k]==0&full_matrix[k,j]==0){
          mean_s_matrix<-rbind(mean_s_matrix,c(i,j,k))
          mean_s=mean_s+1}
           
  }}}

mean_s
mean_s_matrix

```

```{r}

#median
full = s641_full_data_frame
for (i in 1:nrow(full)){
  if (full[i,3]>0)
    full[i,"social_1"]=1
  else
    full[i,"social_1"]=0
}

for (i in 1:nrow(full)){
  if (full[i,4]>0)
    full[i,"task_1"]=1
  else
    full[i,"task_1"]=0
}

median_social<-median(data.frame(subset(full,full["social_1"]>0)["social_tie"])[,1])
median_task<-median(data.frame(subset(full,full["task_1"]>0)["task_tie"])[,1])

for (i in 1:nrow(full)){
  if (full[i,3]>median_social)
    full[i,"social_new_median"]=20
  else if (full[i,3]<=median_social&full[i,3]!=0)
    full[i,"social_new_median"]=1
  else
    full[i,"social_new_median"]=full[i,3]
}


for (i in 1:nrow(full)){
  if (full[i,4]>median_task)
    full[i,"task_new_median"]=20
  else if (full[i,4]<=median_task&full[i,4]!=0)
    full[i,"task_new_median"]=1
  else
    full[i,"task_new_median"]=full[i,4]
}


for (i in 1:nrow(full)){
  if (full[i,"social_new_median"]>=full[i,"task_new_median"])
    full[i,"triad_median"]=full[i,"social_new_median"]
  else
    full[i,"triad_median"]=full[i,"task_new_median"]
}

full_matrix_median<-matrix(nrow=22,ncol=22)
for (i in 1:nrow(full)){
    full_matrix_median[full[i,1],full[i,2]]<-full[i,"triad_median"]
}
median_s<-0
median_s_matrix<-matrix(ncol=3)
for (i in 1:22){
  for (j in 1:22){
    for (k in 1:22){
      if(j>k)
        if (full_matrix_median[i,j]==20&full_matrix_median[i,k]==20 & full_matrix_median[j,k]==0&full_matrix_median[k,j]==0){
          median_s=median_s+1
          median_s_matrix<-rbind(median_s_matrix,c(i,j,k))
          }
  }}}

median_s
median_s_matrix
```



# Question 3
It is also possible to compute betweenness on the edges in a network, as well as the vertices.
These are good measures of flow. Calculate the edge-level betweeness for both of the types
of tie, on the network that considers both social and task ties as being a part of the same
network. Does it seem like edges with high betweenness tend to be strong or weak ties,
according to our two definitions above? Does this result make sense?

# answer: There's no obvious correlation between betweenness and strong/weak ties. I think it make sense because Whether a network satisfies strong triadic closure can depend on the structure of data and the definition of strong/weak relationship. Therefore, the correlation can be different and unobvious.
```{r}

edge.betweenness(social,directed = TRUE)
edge.betweenness(task,directed = TRUE)
full_clean<-subset(full, (social_tie > 0|task_tie > 0))

full_clean_graph<-graph.data.frame(full_clean)
full_clean[,"bw_mean"]<-edge.betweenness(full_clean_graph,directed = TRUE)
full_clean[,"bw_mean"]
for (i in 1:nrow(full_clean)){
  if (full_clean[i,"social_tie"]>=mean_social)
      full_clean[i,"social_1_mean"]=20
  else if (full_clean[i,"social_tie"]==0)
     full_clean[i,"social_1_mean"]=0
  else
     full_clean[i,"social_1_mean"]=1
}


for (i in 1:nrow(full_clean)){
  if (full_clean[i,"task_tie"]>=mean_task)
      full_clean[i,"task_1_mean"]=20
  else if (full_clean[i,"task_tie"]==0)
     full_clean[i,"task_1_mean"]=0
  else
     full_clean[i,"task_1_mean"]=1
}


for (i in 1:nrow(full_clean)){
  if (full_clean[i,"task_1_mean"]>full_clean[i,"social_1_mean"])
      full_clean[i,"mean_tie"]=full_clean[i,"task_1_mean"]
  else
    full_clean[i,"mean_tie"]=full_clean[i,"social_1_mean"]
}


for (i in 1:nrow(full_clean)){
  if (full_clean[i,"mean_tie"]==20)
      full_clean[i,"mean_tie"]=1
  else
    full_clean[i,"mean_tie"]=0
}

cor(full_clean[,"bw_mean"],as.numeric(full_clean[,"mean_tie"]))
plot(full_clean[,"bw_mean"],as.numeric(full_clean[,"mean_tie"]))
     
cor(full_clean[,"bw_mean"],full_clean[,"triad_median"])
plot(full_clean[,"bw_mean"],full_clean[,"triad_median"])

```

#Question 4
Still consider the network that treats both social and task ties as being a part of the same
network. How many pairs of nodes do not have walks between one another? Perform this
calculation directly on the matrix.
##anwer: There are 38 pairs of nodes do not have walks between one another.
```{r}
z<-matrix(0,nrow = 22,ncol = 22)
full_clean_matrix<-data.matrix(full_clean_graph[])
for (i in 1:nrow(full_clean_matrix)){
  for(j in 1:ncol(full_clean_matrix)){
    for (k in 1:22){
      for(l in 1:22){
        if (as.numeric(rownames(full_clean_matrix)[i])==k&as.numeric(colnames(full_clean_matrix)[j])==l)
          z[k,l]=full_clean_matrix[i,j]    
        else z[k,l]==0}}
  }
}

u<-matrix(0,nrow=22,ncol=22)
q<-z
y<-0
while ( y<nrow(z)) { 
  for (i in 1:22){
   for (j in 1:22){
     if (q[i,j]!=0 & u[i,j]==0)
       u[i,j]<-q[i,j]
                }
              }
  y=y+1
  q<-q %*% z}
u
pair<-0

for (i in 1:22){
  for (j in 1:22){
    if (u[i,i]!=0&u[j,j]!=0&i>j& u[i,j]==0&u[i,j]==0){
      pair=pair+1
    }
  }
}
pair

```
#Extra Challenge Problem: 
Generate and plot a network in R in which the network-level measure
of degree centrality is equal to 1, and another where it is equal to 0. Would this hold true for other types of centrality?
##Answer: This holds true for closeness centrality, betweenness centrality, but not true for eigen centrality.
```{r}
inc_1 <- matrix(c(0,1,1,1,1,1,1,1,
                1,0,0,0,0,0,0,0,
                1,0,0,0,0,0,0,0,
                1,0,0,0,0,0,0,0,
                1,0,0,0,0,0,0,0,
                1,0,0,0,0,0,0,0,
                1,0,0,0,0,0,0,0,
                1,0,0,0,0,0,0,0), 8,8) 
inc_1
colnames(inc_1) <- letters[1:8] 
rownames(inc_1) <- letters[1:8] 
inc_graph_1<-graph_from_adjacency_matrix(inc_1)
plot.igraph(inc_graph_1,vertex.label=NA,layout=layout.fruchterman.reingold, 
            vertex.color="orchid1",edge.color="black",vertex.size = 10, 
            edge.arrow.size=.3,edge.curved=FALSE)
centrality_degree_1<-(nrow(inc_1)*7-(7+1*7))/((nrow(inc_1)-1)* ((nrow(inc_1)-2)))
centrality_degree_1
centr_clo(inc_graph_1,mode="all")$centralization
centr_betw(inc_graph_1, directed = FALSE)$centralization
centr_eigen(inc_graph_1, directed = FALSE)$centralization


inc_0 <- matrix(c(0,1,1,1,1,1,1,1,
                1,0,1,1,1,1,1,1,
                1,1,0,1,1,1,1,1,
                1,1,1,0,1,1,1,1,
                1,1,1,1,0,1,1,1,
                1,1,1,1,1,0,1,1,
                1,1,1,1,1,1,0,1,
                1,1,1,1,1,0,1,0), 8,8) 
colnames(inc_0) <- letters[1:8] 
rownames(inc_0) <- letters[1:8] 
inc_0
inc_graph_0<-graph_from_adjacency_matrix(inc_0)

plot.igraph(inc_graph_0,vertex.label=NA,layout=layout.fruchterman.reingold, 
            vertex.color="orchid1",edge.color="black",vertex.size = 10, 
            edge.arrow.size=.3,edge.curved=FALSE)


centrality_degree_0<-(nrow(inc_0)*7-(7*8))/((nrow(inc_0)-1)* ((nrow(inc_0)-2)))
centrality_degree_0
centr_clo(inc_graph_0,mode="all")$centralization
centr_betw(inc_graph_0, directed = FALSE)$centralization
centr_eigen(inc_graph_0, directed = FALSE)$centralization
```

