---
title: "Wenjing Sun HW5"
output:
  html_document:
    df_print: paged
---

#data preparation

```{r}
rm(list = ls(all = TRUE))
library(sna)
library(data.table)
library(ergm)
library(network)
library(plyr)

data<-fread("startup_rounds_and_participants.csv",header=TRUE)

data$startup_id<-as.character(data$startup_id)
data$participant_id<-as.character(data$participant_id)

edge1<-data

# specify the network we'll call net - where dyads are the unit of analysis...
net=network(edge1[,c("participant_id", "startup_id")])

# assign edge-level attributes - dyad attributes
set.edge.attribute(net, "traction", edge1[,"traction"])
set.edge.attribute(net, "round", edge1[,"startup_round_id"])
set.edge.attribute(net, "date", edge1[,"round_record_date"])

# assign node-level attributes to actors in "net"
net %v% "participant_type" = edge1[,"participant_type"]



```

#Question 1
Use the network information provided and an ERGM model to predict whether reciprocation
is more or less likely in this network. What if we only consider connections between startups?
Why does the second model appear different? Include an edges intercept in both models.
```{R}

m1=ergm(net ~ edges + mutual,burnin=15000,MCMCsamplesize=30000,verbose=FALSE)
summary(m1)

exp(m1[1]$coef)

```

```{r}
#only consider connections between startups
edge2<-edge1[,c("participant_id", "startup_id")][which(edge1[,"participant_type"]=="Startup"),]
net_start<-network(edge2)
# assign edge-level attributes - dyad attributes
set.edge.attribute(net_start, "traction", edge1[,"traction"])
set.edge.attribute(net_start, "round", edge1[,"startup_round_id"])
set.edge.attribute(net_start, "date", edge1[,"round_record_date"])

# assign node-level attributes to actors in "net"
net %v% "participant_type" = edge1[,"participant_type"]
m2=ergm(net_start~ edges + mutual ,burnin=15000,MCMCsamplesize=30000,verbose=FALSE)
summary(m2)

lapply(m2[1],exp)

```

#Question 2
Use the network information and an ERGM model to predict whether startups are more
likely to have larger fundraising rounds (i.e., the "has as a participant" relationship is more
likely to exist) if they also participate in more funding rounds. You can run the model on
the entire network or just relationships between startups. In either case, include an edges
intercept as well as a mutuality covariate in the model.

```{r}

net_start1<-network(edge1[,c(1,2)])

net_start1 %v% "degree"=degree(net_start1,"in")

m3<-ergm(net_start1~edges+mutual+nodeicov("degree"))
summary(m3)
lapply(m3[1],exp)


```


#Question 3
Use the network information provided and an ERGM model to predict whether an investor
is more or less likely to participate in a startup's round if it has participated in one of its
rounds in the previous period. Include an edges intercept in the model.

```{r warning=FALSE}
startupid<-unique(edge1[,2])

edge1$Q3<-edge1$participant_id %in% startupid
edge3<-edge1[!is.na(edge1$traction),]

net_start2013<-edge3[year(as.Date(edge3$round_record_date))==2013,]
net2013<-network(net_start2013[,c(1,2)])
set.edge.attribute(net2013, "Q3", net_start2013[,7])
m4 <- ergm(net2013 ~ edges + mutual + edgecov(net2013, attrname = "Q3"))

summary(m4)
exp(m4[1]$coef)

```

#Question 4

Use the network and startup attributes and an ERGM model to predict whether a startup
is more likely to have participants in its rounds that have gained similar levels of traction
in the current period. Then, build a model to predcict whether a startup is more likely to
have participants in its rounds that have gained similar levels of traction using a term for the
current period as well as the previous period. Only consider interactions between startups
in these models, and include an edges intercept in both models.

```{r}
#(1)
net_start2013_4<-merge.data.frame(net_start2013,net_start2013[,c(2,6)],by.x="participant_id",by.y="startup_id")
net_start2013_4<-net_start2013_4[year(as.Date(net_start2013_4$round_record_date))==2013,]
net2013_4<-network(net_start2013_4[,c(1,2)])
set.vertex.attribute(net2013_4, "traction.y", net_start2013_4[,8])
m4_1 <- ergm(net2013_4 ~ edges + mutual + absdiff("traction.y"))

summary(m4_1)
lapply(m4_1[1],exp)


#(2)
net_start4<-merge.data.frame(edge3,edge3[,c(2,6)],by.x="participant_id",by.y="startup_id")
net4 <-network(net_start4[,c(1,2)])
set.vertex.attribute(net4, "traction.p", net_start4[,8])
m5 <- ergm(net4 ~ edges + mutual +  absdiff("traction.p"))
summary(m5)
lapply(m5[1],exp)



```

#Question 5
Of the models run so far, which has the best fit to the actual network? Discuss the model
fit using (1) the built-in mcmc diagnostics, (2) a simulation of the actual network using the
results from the model, and (3) a goodness-of-fit analysis of the estimated model.
```{r}

#m1
m1.sim=simulate(m1,nsim=100);
simnet1=m1.sim[[1]]
mcmc.diagnostics(m1)
plot(simnet1)

#m2
m2.sim=simulate(m2,nsim=100);
simnet2=m2.sim[[1]]
mcmc.diagnostics(m2)
plot(simnet2)



#m3 I think this one is the best model
m3.sim=simulate(m3,nsim=100);
simnet3=m3.sim[[1]]
mcmc.diagnostics(m2)
plot(simnet3)


#m4_1
m4_1.sim=simulate(m4_1,nsim=100);
simnet4_1=m4_1.sim[[1]]
mcmc.diagnostics(m4_1)
plot(simnet4_1)


#m4
m4.sim=simulate(m4,nsim=100);
simnet4=m4.sim[[1]]
mcmc.diagnostics(m4)
plot(simnet4)


#m5
m5.sim=simulate(m4,nsim=100);
simnet5=m5.sim[[1]]
mcmc.diagnostics(m5)
plot(simnet5)



```


#Extra challenge problem
RSiena provides a similar function to ERGM, but is more tailored
for longitudinal data. Re-run the longitudinal models above (Questions 3, 4) using RSiena to
determine if RSiena and ERGM produce similar results.

```{r}
library(RSiena)




```

